# Results

## RQ1. Reasons for Constructing Induction Support Systems

In answering the first research question, I found three reasons that new teachers construct induction support systems: change, scarcity of resources, and conflicting teaching beliefs. These themes were discussed by multiple interviewees (Table 2).

**Table 2.** *Reasons for Constructing Induction Support Systems*

```{r, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table2 <- data.frame(
  Reason = c(
    "Change",
    "Scarcity of resources",
    "Conflicting teaching beliefs"
  ),
  Amelia = c(
    "+",
    "+",
    ""
  ),
  Anne = c(
    "+",
    "+",
    "+"
  ),
  Blair = c(
    "+",
    "+",
    ""
  ),
  Hallie = c(
    "+",
    "+",
    "+"
  ),
  Julie = c(
    "+",
    "+",
    "+"
  ),
  Mike = c(
    "",
    "",
    ""
  ),
  Simone = c(
    "+",
    "+",
    "+"
  ),
  Taylor = c(
    "",
    "",
    ""
  ),
  Wallace = c(
    "+",
    "",
    ""
  )
)

knitr::kable(table2,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 14) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE)
```

### Change

Although some of the changes, disruptions, and uncertainty experienced by new teachers are inevitable parts of transitioning into a new career, all but two new teachers identified additional challenges related to this theme. Several interviewees described these changes in representative ways. For instance, Simone noted that the field of education is constantly in flux, and so inevitably there are additional professional development sessions to attend. Anne and Simone were both handed new curricula each year, and to them it felt like the process of adjusting to a new plan never seemed to stop. Although summer planning seemed to help, Amelia, as an itinerant music teacher, did not receive her final teaching assignments until October. Meanwhile, Julie and Wallace started their teaching careers mid-year, so they entered situations where students’ experiences had been disrupted by the previous teacher’s departure. As a final example, Anne experienced a high degree of personnel turnover in her under-resourced school, even in her first few years of teaching. She had to adjust to a new principal at the start of her third year, and her grade-level partner teacher also left in the middle of that year.

### Scarcity of Resources

Most new teachers constructed induction support systems because of a scarcity of resources. This theme was particularly pronounced for two teachers: Anne and Amelia described numerous challenges related to scarcity: absence of curriculum, missing classroom materials, poor physical conditions in the school, and a limited budget for teaching supplies. The physical environment in Anne’s school created an especially difficult setting for work. Her classroom, a modular trailer, lacked insulation to keep out cold Midwestern U.S. winter winds and hosted bugs, requiring her to store personal belongings in sealable plastic bags during the day. Amelia, as an itinerant music teacher serving several schools in a suburban district, lacked a home classroom and had to teach with whatever supplies she could carry around with her.

### Conflicting Teaching Beliefs

Nearly half of new teachers also described tension between their previously held beliefs about teaching and those encountered in the schools where they worked. Several of their comments were representative. For instance, Julie experienced dissonance with her school’s strict policy on classroom management and student discipline, and she voiced her concerns to her principal:

>I'm only going to do RTC [Responsible Thinking Classroom] when it gets to this point. I'm not going to do RTC every single day. That's just not something that I can justify. And for a lot of those kids, it doesn't work. I don't really see the success in it.

Hallie, in her first year as a teacher, described conflict with more experienced colleagues: “I have one teacher who just wants to use curriculum from 30 years ago. And I'm just like, ‘I can't do it.’ There are just completely irrelevant things.” Hallie also advocated for the inclusion of more anti-racism materials throughout the year, not just confined to Black History Month in February.

## RQ2. Tools in New Teachers’ Induction Support Systems

In answering the second research question, I found three categories discussed by each interviewee: tools for planning, tools for enacting practice, and tools for connecting socially. Each of these categories was voiced by all interviewees (Table 3). These tools were all *self-directed* (i.e., voluntary and informal), meaning that new teachers pursued them in addition to required induction programs (e.g., district professional development workshops, assigned mentor teachers, professional learning communities [PLCs]). Wallace articulated why he put in the extra work: “I just can't think of a time that I didn't ask someone for help… I can't think of any time that I would just fail and just accept it and not reach out.” In the following paragraphs, I describe these tools in more detail.

**Table 3.** *Tools in New Teachers’ Induction Support Systems*

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table3 <- data.frame(
  Tools = c(
    "Planning",
    "Enacting practice",
    "Connecting socially"
  ),
  Amelia = c(
    "+",
    "+",
    "+"
  ),
  Anne = c(
    "+",
    "+",
    "+"
  ),
  Blair = c(
    "+",
    "+",
    "+"
  ),
  Hallie = c(
    "+",
    "+",
    "+"
  ),
  Julie = c(
    "+",
    "+",
    "+"
  ),
  Mike = c(
    "+",
    "+",
    "+"
  ),
  Simone = c(
    "+",
    "+",
    "+"
  ),
  Taylor = c(
    "+",
    "+",
    "+"
  ),
  Wallace = c(
    "+",
    "+",
    "+"
  )
)

knitr::kable(table3,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 14) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE)
```

### Tools for Planning

Each interviewee described seeking planning tools, which included generating ideas, creating curriculum, writing lesson plans, and finding appropriate resources. For instance, Taylor and Blair, the only two interviewees without undergraduate teacher preparation, struggled with creating a semester-long teaching plan. As a result, they sought supports earlier in the planning process, asking for help from their in-school PLCs and social media connections. The remaining interviewees did have undergraduate training, but they also had difficulty in planning. For instance, because her district did not assign a set curriculum to follow, Hallie wrestled internally when planning: “What am I supposed to do? Like, what do you actually want me to do?” She also acknowledged the openness of her colleagues, but limitations remained: “There are teachers that are willing to help, but because my team doesn't do a lot of the actual same activity, it doesn't really help to share planning resources, always.” Hallie made some decisions independently, and at times she also turned to social media for supports. Taking a slightly different approach than the other interviewees, Julie tended to look for supports toward the end of her planning process. She turned to social media to refine an existing plan to add “some extra TeachersPayTeachers flair.”

Some new teachers also struggled with the opposite problem: having too many planning resources. This necessitated navigating an overwhelming number of possibilities of what and how to teach. At times, interviewees found themselves inundated with unfiltered ideas and resources from school colleagues. For instance, Julie described the effect of being offered too much planning help: “I felt like a lot of teachers were saying, ‘Here, try this. Here, try this.’ And I didn't really have the time to fully plan out units or plan out weeks at all.” Julie said she would have preferred to access planning supports only when she needed them, rather than the overwhelming, unidirectional flow of ideas from colleagues to her.

### Tools for Enacting Practice

All interviewees also sought tools for enacting practice, looking to improve instruction and interactions with students in the classroom. For instance, Amelia, Anne, and Julie each talked extensively with colleagues, mentor teachers, and principals about difficult classroom management situations they had encountered and how they navigated these. As another representative example, Hallie discussed with her PLC “embedding real learning ideas” in discussions of current events like voting instead of abstractly “reading a story and making it work with a standard.” She observed that the process of improving her teaching practice benefitted both her and her students: “I enjoy my job a lot more teaching real things, and I think students come away with it more than just memorizing, and being able to do a standard on a standardized test.” New teachers also went to social media occasionally for tools for enacting practice. For instance, Taylor found YouTube videos to be especially useful for demonstrating activities to her physical education (PE) classes.

### Tools for Connecting Socially

Finally, all new teachers also reported positive social benefits of connecting socially with colleagues through grade-level or subject-specific PLCs in a school, and they looked for tools that helped reinforce these relationships as well as form new social connections. As particularly strong example, Taylor’s PE department shares an office space where teachers convene regularly throughout the day. Taylor described this PLC as a “tight-knit group” with a “group mentality” that functions not just as a source of teaching ideas, but a loyal and supportive in-group. When she needed help, her PLC was the first place Taylor looked. Interviewees also described benefits of using social media to connect with others. Anne appreciated being able to vent her frustrations with people beyond her immediate context, and Simone noted the benefits of hearing perspectives and diverse opinions from those outside her local area.

## RQ3. People in New Teachers’ Induction Support Systems

In answering the third research question, I found that new teachers connected with people both within their local school as well as beyond when constructing support systems during induction. These relational themes were discussed by each interviewee (Table 4), and I describe them further in the following paragraphs.

**Table 4.** *People in New Teachers’ Induction Support Systems*

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table4 <- data.frame(
  People = c(
    "In-school",
    "Out-of-school"
  ),
  Amelia = c(
    "+",
    "+"
  ),
  Anne = c(
    "+",
    "+"
  ),
  Blair = c(
    "+",
    "+"
  ),
  Hallie = c(
    "+",
    "+"
  ),
  Julie = c(
    "+",
    "+"
  ),
  Mike = c(
    "+",
    "+"
  ),
  Simone = c(
    "+",
    "+"
  ),
  Taylor = c(
    "+",
    "+"
  ),
  Wallace = c(
    "+",
    "+"
  )
)

knitr::kable(table4,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 14) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE)
```

### In-school Connections

Each interviewee connected with colleagues inside their school building when constructing induction support systems. These people were associated with formally required parts of their support systems (e.g., mentor teachers, PLCs) as well as informal opportunities voluntarily initiated by the new teacher, such as talking to colleagues in the teachers’ lounge. Occasionally, these in-school relationships were reinforced through social media platforms (e.g., Blair and Wallace connected with coworkers on Facebook).

### Out-of-school Connections

Each new teacher also connected with people beyond their school buildings, whether local or more far-reaching, when constructing induction support systems. Some districts required formal gatherings for new teachers, such as district-wide professional development workshops. Amelia’s district offered optional connections through a district-wide Facebook group for sharing resources and a Microsoft Teams account where teachers could talk between official meetings. More than half of the new teachers interviewed (Amelia, Anne, Hallie, Mike, and Wallace) had friends and family members who were also educators, and they would look to these personal connections for informal support. 

Interviewees also joined groups organized to support teachers. For example, during her undergraduate years, Simone became a member of a sorority for African American women, and after graduation, she continued to attend local gatherings of sorority sisters in her city. Many sorority members are also teachers, and Simone found them to be an important source of emotional and professional encouragement as she started teaching. Mike was a member of a national organization that provided focused professional development for new teachers, and he also regularly attended a local gathering of new teachers that was organized in partnership between his district and the teacher preparation program at the nearby university. These examples are types of distributed networks, which extend beyond a teacher’s school building but still rely on face-to-face meetups.

Finally, interviewees often connected with people online as part of constructing their induction support systems. They looked to social media for opportunities to vent their frustrations, seek solidarity, exchange ideas, and find resources—often with an explicit appreciation that these connections were not local.

## RQ4. Social Media as Spaces for Constructing Induction Support Systems

In answering the fourth research question, I found three themes related to how new teachers use social media as spaces for constructing induction support systems. First, new teachers identified numerous possibilities for constructing induction support systems in social media spaces, spanning many platforms. Second, interviewees emphasized the importance of maintaining boundaries around their social media use, even for professional learning. Third, new teachers engaged with social media supports in various ways: browsing, asking, and exchanging.

New teachers decided how to use social media for professional purposes largely on their own. Only one interviewee (Taylor) was familiar with their school’s social media policy for teachers. Even then, she only knew about the policy because a teacher had been fired recently for violating it. This means that schools and districts were not providing guidance to teachers (or the guidance given was not making an impression on new teachers) regarding their use of social media, let alone offering recommendations of best practices to teachers desiring to expand induction support systems through social media.

### Possibilities for Constructing Induction Support Systems in Social Media Spaces

New teachers used numerous social media platforms when constructing induction support systems that incorporated a variety of people from inside and outside their schools (Table 5). Interviewees described how they took into consideration the features of various social media platforms to maximize the benefits of use.

**Table 5.** *Social Media Platforms in New Teachers’ Induction Support Systems*

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table5 <- data.frame(
  Platform = c(
    "Google Classroom",
    "Blogs", "Email listserv", "Facebook", "Instagram", "Microsoft Teams", "Pinterest", "TeachersPayTeachers", "Twitter", "YouTube",
    "Facebook", "YouTube",
    "Facebook",
    "Facebook", "Instagram", "Twitter"
  ),
  Amelia = c("", "+", "", "+", "", "+", "", "+", 
             "", "", "", "", "", "", "", ""),
  Anne = c("", "", "", "", "+", "", "+", "+", 
             "", "", "", "", "", "+", "+", ""),
  Blair = c("", "+", "+", "", "", "", "", "", 
             "+", "+", "", "", "+", "+", "", "+"),
  Hallie = c("", "", "", "+", "", "", "+", "+", 
             "", "", "", "", "", "", "", ""),
  Julie = c("", "", "", "", "+", "", "", "+", 
             "", "", "", "", "", "", "", ""),
  Mike = c("", "+", "", "", "", "", "+", "+", 
             "+", "", "", "", "", "+", "", ""),
  Simone = c("", "", "", "+", "+", "", "", "+", 
             "", "", "+", "", "", "+", "", ""),
  Taylor = c("", "+", "", "", "+", "", "", "+", 
             "", "+", "", "+", "", "", "", ""),
  Wallace = c("+", "", "", "+", "", "", "+", "+", 
             "", "", "", "", "+", "+", "", "")
)

knitr::kable(table5,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 12) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE) %>%
  pack_rows("Planning, in-school", 
            1, 1, 
            label_row_css = "background-color: #23373B; color: #fff;") %>%
  pack_rows("Planning, out-of-school", 
            2, 10, 
            label_row_css = "background-color: #23373B; color: #fff;") %>%
  pack_rows("Enacting practice, out-of-school", 
            11, 12, 
            label_row_css = "background-color: #23373B; color: #fff;") %>%
  pack_rows("Connecting socially, in-school", 
            13, 13, 
            label_row_css = "background-color: #23373B; color: #fff;") %>%
  pack_rows("Connecting socially, out-of-school", 
            14, 16, 
            label_row_css = "background-color: #23373B; color: #fff;")
```

New teachers talked most frequently about using social media to seek planning tools from out-of-school connections. All of the interviewees named multiple social media platforms they found to be helpful for this purpose. New teachers seemed to especially appreciate content-sharing platforms where others regularly shared educational resources: TeachersPayTeachers.com, Instagram, Pinterest and YouTube. Mentioned less often, but still important, were social media platforms where new teachers could easily ask questions to request specific supports (e.g., Facebook, Twitter, Microsoft Teams).

Social media platforms also offered the possibility of seeking planning tools from in-school connections, but this affordance was mentioned by only one interviewee. Wallace described how peer 10th-grade English teachers in his school used a Google Classroom shell (i.e., a blank template in a learning management system) as a repository for sharing ideas and resources with each other.

In addition, two new teachers discussed how social media help reinforce local relationships by offering opportunities to find tools for connecting socially with in-school colleagues. For instance, Wallace worked at his school for several years as a staff member prior to being hired to teach midyear. Because of his prior experience, he was connected to many school colleagues on Facebook. He believed that this additional layer of personal connection (e.g., seeing photos of coworkers’ children) made it easier for him to ask coworkers for help during his transition into teaching.

Much more often, interviewees discussed how they used social media to make social connections beyond their local school. For instance, Anne described the helpfulness of venting outside her local context, where so many of her frustrations stemmed: “A lot of times, if I go to social media, it's for an outlet, for frustrations, and difficulties.” Simone participated in a Facebook group of teachers from all over the U.S., and she appreciated the perspective of being able to see “what other teachers are dealing with in their district or their state like, ‘Are you, are you experiencing these same things?’ And they are, and it's nice to know that you're not the only one.” She appreciated being reminded that she was not alone feeling the way she did, and that there were other ways to teach besides what she had experienced in her own school and district. These perspectives seemed particularly important to Simone as a Black teacher whose preparation program had been overwhelmingly white, and whose school of employment was diverse but under-resourced.

Finally, two new teachers (Taylor and Simone) described using social media to find tools for enacting practice from out-of-school connections. Taylor subscribed to a PE teacher’s YouTube channel to get inspiration for her own classes. YouTube’s video medium was particularly useful for her to be able to see demonstrations of activities (e.g., drills, games) that she could facilitate in her own PE classes. The teacher Facebook group in which Simone was a member had a culture where “asking questions, asking if we deal with this or do you have any suggestions” was common, and this helped Simone think through issues in her own classroom. None of the interviewees linked their use of social media to tools for enacting practice from in-school connections, so that purpose is absent from Table 5.

### Boundaries Around Social Media Use

In addition to the possibilities afforded by social media as spaces for constructing induction support systems, new teachers noted several important boundaries they tried to maintain around their social media use: personal-professional separation, time management, and social comparison. These boundary themes were discussed by a subset of interviewees (Table 6). 

**Table 6.** *Boundaries Maintained by New Teachers on Social Media*

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table6 <- data.frame(
  Boundary = c(
    "Personal-professional separation",
    "Time management",
    "Social comparison"
  ),
  Amelia = c(
    "+",
    "",
    ""
  ),
  Anne = c(
    "+",
    "",
    "+"
  ),
  Blair = c(
    "+",
    "",
    ""
  ),
  Hallie = c(
    "+",
    "+",
    ""
  ),
  Julie = c(
    "+",
    "",
    ""
  ),
  Mike = c(
    "+",
    "+",
    "+"
  ),
  Simone = c(
    "+",
    "+",
    ""
  ),
  Taylor = c(
    "+",
    "",
    ""
  ),
  Wallace = c(
    "+",
    "",
    ""
  )
)

knitr::kable(table6,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 14) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE)
```

First, each interviewee described how maintaining separation between their personal and professional lives on social media was important to them. For instance, Hallie and Simone were more compelled by maintaining personal-professional boundaries than maximizing social media benefits, and they chose to limit their social media use for this reason. Julie compartmentalized, using some social media platforms for personal reasons and others for professional purposes. She succinctly summed up the benefit of this approach: “I know what I'm getting myself into when I open each one of the apps.”

Time management for social media use was another important boundary for three interviewees. For instance, Simone had been actively working on improving her time management skills, with a goal of not bringing work home with her. This meant she was less inclined to voluntarily use social media in the evening for professional learning. Similarly, Mike was very time-conscious and deliberate in limiting his social media use: “If I don't have time for myself, then I'm doing [my students] a disservice. I have to have that shut-off button.”

Anne and Mike named a third set of boundaries they believed were important to maintain: those around unhelpful social comparisons. Anne, teaching in an under-resourced school with a challenging physical environment, noted how unhelpful it was to compare herself to teachers in other districts who posted photos of their pristine classrooms on social media:

>Back to the Instagram thing, I do follow some teacher accounts. Sometimes I feel like, it makes me feel like a crappy teacher, because I'm seeing them do all these things. And I'm like, “I'm tired right now. If I did all those things, I would either never sleep, or I would be just doing those things. I wouldn't be able to follow through with them and actually teach with those tools that they're spending hours making on the weekend.” And it just, it makes me feel like I should be doing more. But I already feel like I'm doing more than I can keep up with.

Anne found that the visual, highly curated nature of Instagram drew her into unrealistic expectations for herself and demotivated her to construct an induction support system. Because of these unhelpful social comparisons, she decided to limit her Instagram use. Mike described a similar issue when seeing his best friend’s Facebook posts. The income level and number of vacation days inferred from his friend’s travel photos caused Mike to question his own choice of a teaching career. He named these feelings of envy as another reason for limiting his time on social media.

### Ways of Engaging on Social Media

In addition to the possibilities afforded by social media and important boundaries to maintain around them, new teachers also described several distinct ways of engaging on these platforms: browsing, asking, and exchanging. All interviewees described browsing on social media but asking and exchanging were less common (Table 7).

**Table 7.** *Ways New Teachers Engage on Social Media*

```{r, tidy=TRUE, include=TRUE, echo=FALSE}
table7 <- data.frame(
  Engagement = c(
    "Browsing",
    "Asking",
    "Exchanging"
  ),
  Amelia = c(
    "+",
    "+",
    "+"
  ),
  Anne = c(
    "+",
    "+",
    "+"
  ),
  Blair = c(
    "+",
    "+",
    ""
  ),
  Hallie = c(
    "+",
    "",
    ""
  ),
  Julie = c(
    "+",
    "+",
    ""
  ),
  Mike = c(
    "+",
    "+",
    ""
  ),
  Simone = c(
    "+",
    "+",
    "+"
  ),
  Taylor = c(
    "+",
    "",
    ""
  ),
  Wallace = c(
    "+",
    "",
    "+"
  )
)

knitr::kable(table7,
             booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width=TRUE, font_size = 14) %>%
  kableExtra::column_spec(1, bold=TRUE, border_right=FALSE)
```

First, each new teacher engaged by *browsing* on social media, which included activities such as searching for resources on TeachersPayTeachers.com, watching YouTube videos, and scrolling through Pinterest. Browsing was not necessarily a passive form of participation. For instance, Julie was active and purposeful: “I feel like I filled a lot of gaps. If I couldn't find something, I'd go to social media to find it.” Amelia started with a specific need in mind, visiting to TeachersPayTeachers.com to find lesson plans for substitute music teachers. To save time, Mike developed a system that would allow him to skim through Pinterest more quickly: “I don't engage with it, I don't go on and search for things. I have it set up where it sends me one email a day with about 10 different math activities or blog posts.” Despite benefitting from browsing social media, Wallace apologized in his interview for being a “taker;” he felt bad that he was not contributing, not giving back to others.

Second, two-thirds of the interviewees engaged on social media by *asking*, which included posting about specific resources needed. For instance, Julie expressed a desire for more of this: “I wish there was more a way to use social media like, ‘Here's a problem I'm dealing with; can people help me with this problem?’” Amelia described several such opportunities, albeit confined to her local school district. She participated in a Facebook Group composed of music teachers in her district, where colleagues could post questions and requests for sharing musical instruments between classrooms. Amelia’s PLC included teachers from 10 schools and, at the time of our interview, had just begun using Microsoft Teams as “a way for us to meet and actually talk about stuff… a way for us to communicate in the interim between our two-week meetings.” For Amelia, both the Facebook Group and Microsoft Teams were spaces where she could ask for what she needed.

Third, nearly half of new teachers engaged on social media by *exchanging*, which included seeking supports through interaction and dialogue to satisfy mutual interests. This type of engagement was characterized by group membership. The practice of asking was present here as well, but exchange also included contributing ideas, giving advice, and conversing to determine best practices. For instance, even as a new teacher, Simone found that she was able to give well-received advice in a teacher Facebook group. 
